Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-09 paper.tex
Start my work on writing draft.
- Convert some of the "against" section to essay/paragraph form.
- Add some notes for later
- Add some sources
- Add a quote that could be useful in our final thoughts.

\section{Arguments Against Piracy}

\subsection{Access to Dangerous/Illegal Content}
\begin{enumerate}
  \item Piracy generally enables free/open access to information.

  \item This can be a bad thing for dangerous information that can threaten
    lives/livelihoods.

  \item Piracy would facilitate the spread of dangerous information concerning
    national security, with few tools to mitigate and almost none to stop it.

  \item Piracy provides the means to access content that is questionable/illegal.

  \item When you are pirating, you need to be extremely careful with what you
    are getting. Not all sources are trusted sources; software can be infected
    with malware.

  \item Information and content can be dispersed by bad actors.
\end{enumerate}

\subsection{Economic}
\begin{enumerate}
  \item Businesses are losing money because of acts of piracy.
  \item Piracy is theft, in this sense. It is taking away from employee
    benefits and potential tax revenue for the government.

  \item Piracy takes money from creators and organizations behind content
    creation.~\cite{congress:pirating-the-american-dream}

  \item \textcquote{mrad:effects-of-ip}{According to Gould and Gruben (1996), IPRs protection stimulates economic growth if it is
    accompanied by a policy of trade liberalization. By encouraging initiatives to innovate, IPRs
    protection may influence the economic growth of an open country. Park and Ginarte (1997) found
    that IPRs protection affects economic growth indirectly by stimulating the accumulation of
  factors of production such as physical capital and R\&D capital.}

    Piracy discourages innovation in the capitalist marketplace.
\end{enumerate}

\section{Christian Response}

@@

>>>>

\section{Arguments Against Piracy}
While piracy enables free access to information and content, it is crucial to
faithfully and charitably explore the potential dangers and economic
implications associated with this practice. The arguments against piracy are
not easy, nor should be, easy to dismiss. This paper will focus mainly on the
ethical and economical concerns that the use of piracy introduces into society.

\subsection{Access to Dangerous/Illegal Content}
Piracy has been associated with unrestricted access to information and
content. As previously discussed, this aspect of piracy provides the means for
those in need to access information that would otherwise be unavailable to them;
similarly, piracy can thus provide avenues to bypass governmental restrictions
on public information. This same benefit, however, becomes a strong argument
against piracy when what is distributed is dangerous or illegal content.

\subsubsection{Criminality of the Seeder and Leecher}
This paper has focused on a more wholistic definition that encompasses
the tools, techniques, motivations, and content, but the motivations and
content that are involved in piracy should not be ignored. Piracy does involve
a form of theft and dissemination of an individual's or organization's
intellectual property. Piracy, thus can and most often does violate laws in
most jurisdictions. Piracy, when it uses torrenting, involves both the
seeder and the leecher (or the uploader and downloader, if not using torrenting).
Depending on the legislation of the country in question, the leecher may or
may not be found guilty of a crime, but this is complicated by the global
context of digital piracy.

In the United States, the downloader/streamer/leecher are generally considered
offenders that could be subject of fines or even criminal charges. The severity
of the penalties of piracy in these cases pose a major argument against the use
of piracy, at least in the United States or nations where the individual
downloading can be found guilty of a crime. ``Fair use'' and statutes of
limitations may alleviate penalties, but repeat offences may also lose one's
favor in these cases.~\cite{felonies.org}

\subsubsection{Malware}
Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. Some piracy tools provide
some ways to vet the authenticity of an uploader based on past uploads or based
on the user's relationship with the piracy/torrenting
site\footnote{%
  \href{https://pirates-forum.org/Thread-ThePirateBay-Want-Trusted-VIP-Status-Pink-Green-Skull-See-Here}{ThePirateBay},
  for example provides icons to display whether a user is \emph{Trusted},
  \emph{VIP}, or \emph{Moderator}%
}, but not all sites provide these metrics or warnings for the average end-user.
Instead, the burden is often on the end-user, and it is not unfair to assume
that the average person would not be able to analyze downloaded software for
malware.

% TODO: Add an example of malware distributed via piracy

\subsubsection{Illegal content}
Piracy, as discussed above, provides a way to distribute illegal content. This
content is not always beneficial to society; research articles, art, movies, \&c.
are not the only sorts of content that a pirate may distribute. Piracy opens
the door for questionable and illegal content that may be harmful to society
or national security.

% TODO: Talk about ties to illegal organizations that are involved?

\subsection{Economic}
Piracy, as a theft, also causes real harm to businesses. The act of piracy
does involve stealing and distributing content from creators and organizations
that invested time, money, and effort into the content. In this sense, piracy
is stealing from the individuals' revenue and the government's tax
revenue.~\cite{congress:pirating-the-american-dream}

\textcquote{mrad:effects-of-ip}[.]{%
  According to Gould and Gruben (1996), IPRs protection stimulates economic
  growth if it is accompanied by a policy of trade liberalization. By
  encouraging initiatives to innovate, IPRs protection may influence the
  economic growth of an open country. Park and Ginarte (1997) found that IPRs
  protection affects economic growth indirectly by stimulating the accumulation
  of factors of production such as physical capital and R\&D capital%
}
Piracy, therefore, discourages innovation in the capitalist marketplace.

% TODO
\section{Christian Response}
A Christian response to piracy should honestly take into account both sides of
the debate. As shown above, piracy does have some merit to it. Christians have
to admit that piracy-promoting tools do enable

% 1 Peter 2:13-17
% Romans 13:4-5

@@

\begin{displayquote}
  Of additional concern is the fact that by making \textins{Intellectual Property}
  theft a national security threat without being clear about what actually
  constitutes intellectual property, not only does the U.S. government create a
  new reason for a militarized Internet, but it also sets the stage for companies
  to assert that a range of other activities from file sharing to producing
  counterfeit DVDs threaten national security and require further state
  intervention.~\cite[p. 264]{halbert:agendas}
\end{displayquote}
